Analyzing the impact of social attributes on the success of commit integration

### 2017-02-18 Paper/MSRChallenge2017.tex
minor change
forgot to update the introduction

Our study shows that social factors are an important aspect of build success but
these factors alone do not fully predict if a build will succeed.  We also show
that core team members are more likely to achieve build success than non-core
team members.

@@

The follower results indicate that developers with more followers are more
likely to pass the build, although followers are not a perfect indicator.
Developers with over 1000 followers had more than a 10\% increase compared to
developers with no followers.  This shows that high-quality developers are more
likely to have a large number of followers.

>>>>

Our study shows that social factors are an important aspect of build success but
these factors alone do not fully predict if a build will succeed.  We also show
that core team members are more likely to achieve build success than non-core
team members and having followers increases the likelihood passing the
continuous integration build.

@@

The follower results indicate that developers with more followers are more
likely to pass the build, although followers are not a perfect indicator.
Developers with over 1000 followers had more than a 10\% increase compared to
developers with no followers.  This shows that higher quality developers are more
likely to have a large number of followers.
